Results

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
rephrasing one sentence

To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)). <!--JZ: Vielleicht wäre hier eine Heatmap auch ganz nice, das scheint wohl eine gute Visualisierung für einen Chi Square Test zu sein (https://www.analyticsvidhya.com/blog/2021/06/decoding-the-chi-square-test%E2%80%8A-%E2%80%8Ause-along-with-implementation-and-visualization/)-->

>>>>

To investigate the ecological validity of the calculated subjective values of ER strategies, we tested whether SVs were associated with the actual choice of participants in the last experimental block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)). <!--JZ: Vielleicht wäre hier eine Heatmap auch ganz nice, das scheint wohl eine gute Visualisierung für einen Chi Square Test zu sein (https://www.analyticsvidhya.com/blog/2021/06/decoding-the-chi-square-test%E2%80%8A-%E2%80%8Ause-along-with-implementation-and-visualization/)-->
